---
title: "FB CEO Hearings Wordclouds"
author: "Bo Suzow"
date: "April 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## FaceBook CEO Senator/House of Rep Hearings
On April 10 & 11, 2018, Congressional hearings were held in which FaceBook CEO exchanged questions and answers with US lawmakers.  The transcripts of the both hearings are publicly available at the Washington Post website ([full transcript for Day 1 hearing ]("https://www.washingtonpost.com/news/the-switch/wp/2018/04/10/transcript-of-mark-zuckerbergs-senate-hearing/?utm_term=.3a46cd6da4a1"), [partial transcript for Day 2 hearing]("https://www.washingtonpost.com/news/the-switch/wp/2018/04/11/transcript-of-zuckerbergs-appearance-before-house-committee/?utm_term=.300276ffbe68"))

This article utilizes The transcripts textual data that has been downloaded and processed in Python (3.6) code. The sanitized word tokens are stored in FB_CEO.txt.


```{r}
# read the work tokens file.


# create a corpus from the tokens
library(tm)
fname="FB_CEO.txt"
FB.text = readLines(fname)
text.corpus <- Corpus(VectorSource(FB.text))

# plot a wordcloud

library(wordcloud)
#generate wordcloud
wordcloud(text.corpus,
          min.freq = 2, 
          scale=c(7,0.5),
          colors=brewer.pal(8, "Dark2"), 
          random.color= TRUE, 
          random.order = FALSE, 
          max.words = 300)
```